---
# latex commands: '|' for line breaks; '\vspace' to define vertical spacing (- to reduce
# vertical spacing); '\hspace' do the same for horizontal spacing; '\ footnotesize' shrinks
# the text; '\qquad' adds spacing between text so does '\' but to a smaller degree

title: |
    | \huge \vspace{-2.5cm} \hspace{-7cm} **Serial Visual Fields Report**
    | \footnotesize \vspace{0.2cm} \hspace{-8.3cm} \textcolor{gray} {Static Automated Perimetry with the SITA Stamdard Strategy}
    | \footnotesize \vspace{0.05cm} \hspace{-8.3cm} \textcolor{gray} {Size III Stimulus \qquad \qquad \qquad \ \ SUNY-IU Classic NVs for 24-2}

output:
  pdf_document
  
# enable user to define sections of multiple columns with a lot of flexibility
header-includes:
  - \usepackage{multicol}
  - \newcommand{\hideFromPandoc}[1]{#1}\hideFromPandoc{\let\Begin\begin\let\End\end}
  - \setlength{\columnsep}{20pt}
---

<!-- \rule{\textwidth} draws a horizontal line that spans the textwidth -->
\vspace{-1.4cm} \rule{\textwidth}{1pt}

```{r setup, echo = FALSE}
# install.packages("remotes")
# library(remotes)
# install_github("imarinfr/vf1/source")                       # install latest version of visualField package!
# install.packages('RColorBrewer')
library(RColorBrewer)
library(visualFields)

# install.packages('tinytex')                                 # install tinytex to generate pdf output;
library(tinytex)                                              # tinytex is a lightweight LaTeX distribution
     
# read raw data into working directory
full_d <- read.csv('data/power.csv')

# load function to configure data set 
source('code/vf_config.R')
npx <- 30                                           # how many px?
nrow <- 12                                          # how many rows per px series?           
full_d <- vf_config(full_d, npx, nrow)
```

<!-- latex command to remove page number -->
\pagenumbering{gobble}   

\vspace{0.7cm} \Begin{multicols}{3}

```{r echo=FALSE, fig.height=6, fig.width=7}
# compute MDs from each visit for all px series
all_md <- data.frame( px = rep(1:npx, each=nrow),
                      md = getgl(full_d)$tmd )

# function to compute MD range for a specified px series
range <- function(data, px){
                  a <- data[which(data$px == px),]
                  max(a$md) - min(a$md)
                  }

# Compute and store MD range for every px series 
md_range <- vector('numeric', npx)

for(i in 1:npx){
  md_range[i] <- range(data = all_md, px = i)
 }

# What is the maximum MD range? Use this as the model to set ylim for every px!
model_range <- round(max(md_range) + 2, 
               digits = 0)

# isolate a px series (define 'px')
d <- subset(full_d, id==px)

# WHat are the MDs for this specific px that we are plotting?
md <- all_md[which(all_md$px == px), 2]
ylim <- round( 
           c(mean(md) - model_range/2, 
           mean(md) + model_range/2), 
        digits = 0)

par(mar = c(2, 2, 0, 1))

plot(d$date, md,
     bty = 'n',
     xaxt = 'n',
     yaxt = 'n',
     xlab = '',
     ylab = '',
     ylim = ylim)

# add a huge 'MD' in the backround
text(mean(d$date),
     mean(md),
     labels = 'MD',
     cex = 12,
     col = 'gray96')

# add OLSR line
lm.model <- lm(md~date, data = d)
slope <- summary(lm.model)$coefficients[2]

if (slope < 0){
  line_col <- 'red'
   } else 
     {line_col <- 'green'}

abline(lm.model, lwd = 4, col = line_col)

# replot points so they are not obscured by 'MD' and OLSR
points(d$date, md,
       pch = 19,
       cex = 4,
       col='maroon')

# Configure X axis
xaxis <- seq(min(d$date), max(d$date), length.out = 5)
axis(side = 1,
     tick = FALSE,
     col.axis = 'gray56',
     cex.axis = 1.8,
     at = xaxis,
     labels = format(xaxis, '%b %y') )

# Configure Y axis
yaxis <- seq(min(ylim), max(ylim), 1)
par(las = 1)
axis(side = 2,
     tick = FALSE,
     col.axis = 'gray56',
     cex.axis = 2.2,
     at = yaxis,
     labels = yaxis )

# add very faint horizontal ref lines
abline(h = yaxis, col = 'gray95')
```


```{r echo=FALSE, fig.height=6, fig.width=7}
# add sparkline plot
vfplotsparklines(d, lwd = 3)
```

```{r include=FALSE}
# compute PSD
psd <- getgl(d)$psd
```

<!-- lines 152 - 162 are for show px details: MD, PSD, ID, AGE, FPR & FNR -->
<!-- '\hfill' is used to push text to the document margins; \small makes text small; \scriptsize even smaller -->

| \ \ \ \quad  \scriptsize \textbf {ID: \hfill \small `r px`}

| \ \qquad  \scriptsize \textbf {AGE: \hfill \small `r round(mean(d$age), digits = 1)` \quad|\quad `r min(d$age)` to `r max(d$age)`}   

| \ \qquad  \scriptsize \textbf {MD: \hfill \small `r round(mean(md), digits = 1)` \quad|\quad `r round(min(md), digits = 1)` to `r round(max(md), digits = 1)`}

| \ \qquad  \scriptsize \textbf {PSD: \hfill \small `r round(mean(psd), digits = 1)` \quad|\quad `r round(min(psd), digits = 1)` to `r round(max(psd), digits = 1)`}

| \ \qquad  \scriptsize \textbf {FPR:  \hfill \small `r round(mean(d$fpr), digits = 1)` \quad|\quad `r round(min(d$fpr), digits = 1)` to `r round(max(d$fpr), digits = 1)`}

| \ \qquad  \scriptsize \textbf {FNR: \hfill \small `r round(mean(d$fnr), digits = 1)` \quad|\quad `r round(min(d$fnr), digits = 1)` to `r round(max(d$fnr), digits = 1)`}

\End{multicols}


\vspace{0.1cm}
\hfill -----------------
\vspace{0.1cm}

<!-- lines 173 to 206 make grayscale plots (maximum 12 plots) and also a date column on the right-hand side -->

```{r echo=FALSE, fig.width=35, fig.height=7}
# Function to plot a row of 3 VF grayscale plots and a date column
makerow <- function(first_vf, last_vf){
           par(mfrow = c(1,4), xpd = TRUE)
  
           for(i in first_vf : last_vf){ vfplot(d[i,], 's') }
  
           plot.new()
           
           legend('right', 
                  bty = 'n', 
                  legend = format(d$date[first_vf : last_vf], '%d %b %Y'),
                  cex = 6,
                  y.intersp = 3,
                  text.col = 'gray56')
}

makerow(first_vf = 1, last_vf = 3)
```


```{r echo=FALSE, fig.width=35, fig.height=7}
makerow(first_vf = 4, last_vf = 6)
```


```{r echo=FALSE, fig.width=35, fig.height=7}
makerow(first_vf = 7, last_vf = 9)
```


```{r echo=FALSE, fig.width=35, fig.height=7}
makerow(first_vf = 10, last_vf = 12)
```

\vspace{0.3cm} \rule{\textwidth}{0.01pt}

\hfill \footnotesize \textcolor{gray} {Printed: `r format(Sys.Date(), '%d %b %Y') `}




